Analysis datasets

### 2022-12-21 analysis_backup/supplementary-materials/analysis_datasets.Rmd
- Commit after hard reset

---
title: "Petrography dataset"
output: pdf_document
---

@@

library(knitr)
library(kableExtra)

@@

  kableExtra::landscape() %>% 

>>>>

---
title: "Analysis datasets"
author: "Belmiro et. al"
output: pdf_document
classoption: landscape
---

@@

knitr::opts_chunk$set(echo = FALSE, message = FALSE)

```{r callpackages}

library(readr)
library(knitr)
library(kableExtra)

```{r calldb}

macro_dataset <- read_csv("../data/supplementary_data/macroscopic_dataset.csv")

knitr::kable(head(macro_dataset [1:3], 25), booktabs = TRUE, longtable = TRUE, caption = "Dataset for macroscopic description of the geological samples.") %>% 
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "12cm") %>% 
  kable_styling(font_size = 9) %>% 
  kable_styling(latex_options = c("repeat_header","hold_position"))

@@
